Combinatorial Cascading Bandits with contextual information and position discounts

### 2016-01-26 contextual combinatorial cascading bandits.tex
update experiment

% experiment - synthetic - results
\begin{figure*}
	\centering
	\subfigure[Disjunctive, $\gamma=1$]{
		\includegraphics[height = 3 cm, width = 4 cm]{synD-T5-L100-K4-1.eps}}
	\subfigure[Disjunctive, $\gamma=0.9$]{
		\includegraphics[height = 3 cm, width = 4 cm]{synD-T5-L100-K4-9.eps}}
	\subfigure[Conjunctive, $\gamma=1$ ]{
		\includegraphics[height = 3 cm, width = 4 cm]{synC-T10000-L100-K4-1.eps}}
	\subfigure[Conjunctive, $\gamma=0.95$ ]{
		\includegraphics[height = 3 cm, width = 4 cm]{synC-T10000-L100-K4-95.eps}}
	\caption{Synthetic Data Set, L=100, K=4, d=10}
	\label{fig:synthetic} % 用于交叉引用
\end{figure*}

@@

We experiment on four settings. Under each setting, the learning agent chooses a set of $K$ items out of $L$ ground items. The first two are of the disjunctive objective where the learning agent observes from the first one of the chosen $K$ items until first one with weight $1$; the last two are of conjunctive objective where the learning agent observes from the first item until the first one with weight $0$. Notice that with $\gamma \leq 1$, the oracle to select a feasible action is to select the set of $K$ items with highest UCBs; $\gamma < 1$ will force the items in the optimal action list in the decreasing order of their UCBs and we also use this order when $\gamma = 1$. The results are shown in Fig.~\ref{fig:synthetic} and our algorithm outperforms {\it CombCascade} algorithm because they do not use the context information.

>>>>

% experiment - synthetic - results
\begin{figure*}
	\centering
	\subfigure[Disjunctive, $\gamma=1$]{
		\includegraphics[height = 3 cm, width = 4 cm]{synD-T5-L100-K4-1.eps}}
	\subfigure[Disjunctive, $\gamma=0.9$]{
		\includegraphics[height = 3 cm, width = 4 cm]{synD-T5-L100-K4-9.eps}}
	\subfigure[Conjunctive, $\gamma=1$ ]{
		\includegraphics[height = 3 cm, width = 4 cm]{synC-T5-L100-K4-1.eps}}
	\subfigure[Conjunctive, $\gamma=0.9$ ]{
		\includegraphics[height = 3 cm, width = 4 cm]{synC-T5-L100-K4-9.eps}}
	\caption{Synthetic Data Set, L=100, K=4, d=10}
	\label{fig:synthetic} % 用于交叉引用
\end{figure*}

@@

We experiment on four settings. Under each setting, the learning agent chooses a set of $K$ items out of $L$ ground items. The first two are of the disjunctive objective where the learning agent observes from the first one of the chosen $K$ items until first one with weight $1$; the last two are of conjunctive objective where the learning agent observes from the first item until the first one with weight $0$. Notice that with $\gamma \leq 1$, the oracle to select a feasible action is to select the set of $K$ items with highest UCBs; $\gamma < 1$ will force the items in the optimal action list in the decreasing order of their UCBs and we also use this order when $\gamma = 1$. The results are shown in Fig.~\ref{fig:synthetic} and our algorithm outperforms {\it CombCascade} algorithm because they do not make use of the context information.
